\documentclass{article}
\makeatletter
 \renewcommand{\section}{\@startsection{section}{1}{\z@}%
 {1.5\Cvs \@plus.5\Cvs \@minus.2\Cvs}%
 {.5\Cvs \@plus.3\Cvs}%
 {\reset@font\Large\mcfamily}}
 \makeatother
\usepackage[top=30truemm,bottom=20truemm,left=22truemm,right=22truemm]{geometry}
\usepackage{amsmath, amssymb}
\usepackage{newtxtext,newtxmath}
\pagestyle{empty}

\usepackage{setspace}
\usepackage{hyperref}

\begin{document}
\onehalfspacing

\begin{center}
  \textbf{{\Large Hayato Umetani}}

  \textbf{Email} : 210i005i@stu.kobe-u.ac.jp

\end{center}

\hrulefill

\begin{flushleft}
  \textbf{\large{Education}}
\end{flushleft}

Ph.D. in Graduate School of International Cooperation Studies, Kobe University \hspace{\fill} Apr. 2023--

\ \

Master in Graduate School of International Cooperation Studies, Kobe University \hspace{\fill} Apr. 2021-- Mar. 2023

\ \

Bachelor in Policy Studies / United Nations and Foreign Affairs Studies (Multiple Degrees), Kwansei Gakuin University \textit{summa cum laude} \hspace{\fill} Apr. 2017-- Mar. 2021



\hrulefill

\begin{flushleft}
  \textbf{\large{Research Interests}}
\end{flushleft}

Development Economics, Environmental Economics

\hrulefill

\begin{flushleft}
  \textbf{\large{Publications}}
\end{flushleft}

"Heterogeneous effects of Aid-for-Trade on donor exports: Why is Japan different?" (with Shuhei Nishitateno) \textit{Review of International Economics}, 1–29.

\hrulefill

\begin{flushleft}
  \textbf{\large{Working Papers}}
\end{flushleft}

"Wildfires, Pollution, and Pregnancy Outcomes: Evidence from Lightning Strikes" \ \href{https://dx.doi.org/10.2139/ssrn.4833440}{Download}

\hrulefill

\begin{flushleft}
  \textbf{\large{Ongoing Projects}}
\end{flushleft}

"Wildfires and the Labor Market"

"The Impact of Children's Cafeteria on Child Development" with Kengo Igei and Makiko Nakamuro

\hrulefill

\begin{flushleft}
  \textbf{\large{Presentations}}
\end{flushleft}

\textbf{2025}: University of Tokyo, AERE Summer Conference, ESWC

\textbf{2024}: J-TREE Workshop, Keio University, Musashi University, JEA Annual Meeting (poster), SEEPS Annual Conference, Occasional Workshop in Environmental and Resource Economics (UCSB), OSIPP Lunch Seminar, ISER Moriguchi Prize Seminar, AASLE

\textbf{2023}: SEEPS Annual Conference

\hrulefill

\begin{flushleft}
  \textbf{\large{Relevant Positions}}
\end{flushleft}

\textbf{Research Fellowship for Young Scientists}, Japan Society for the Promotion of Science (JSPS) \hspace{\fill} Apr. 2024 --

\textbf{JST SPRING program student}, Kobe University \hspace{\fill} Apr. 2023 -- Mar. 2024

\textbf{Research Assistant}, Center for Evidence Co-creation \hspace{\fill} Nov. 2023 --

\textbf{Research Assistant} for Jun Goto, Tomoko Matsumoto, Junichi Yamasaki, Kobe University \hspace{\fill} May. 2022 -- Feb. 2024

\textbf{Research Assistant} for Professor Takahiro Ito, Kobe University \hspace{\fill} Oct. 2021 -- Feb. 2022

\textbf{Research Assistant} for Professor Shuhei Nishitateno, Kwansei Gakuin University \hspace{\fill} Sep. 2020 -- Mar. 2021

\textbf{United Nations Youth Volunteer} at UNICEF Vietnam (full-time) \hspace{\fill} Sep. 2018 -- Feb. 2019

\hrulefill

\begin{flushleft}
  \textbf{\large{Teaching Experiences}}
\end{flushleft}

\textbf{Teaching Assistant} for Microeconomics, Graduate School of International Cooperation Studies, Kobe University

Instructor: Takahiro Ito

\hrulefill

\begin{flushleft}
  \textbf{\large{Awards \& Scholarships}}
\end{flushleft}

\textbf{Runner up of the 27th Moriguchi prize}, Osaka University \hspace{\fill} Nov. 2024

\textbf{JASSO Scholarship (full exemption)} \hspace{\fill} Apr. 2021 -- Mar. 2023

\textbf{Scholarship for Doctoral Students}, Kobe University \hspace{\fill} Mar. 2023

\textbf{SPS Award Top 10}, Kwansei Gakuin University, award for students with the top 10 GPA \hspace{\fill} Mar. 2018/2020/2021

\textbf{Ambo Award}, Kwansei Gakuin University, award for senior thesis \hspace{\fill} Mar. 2021

\textbf{Kojima Award}, Kwansei Gakuin University, award for junior thesis \hspace{\fill} Mar. 2020

\textbf{Industry-Academia Partnership Ikuei Scholarship}, Kwansei Gakuin University \hspace{\fill} Mar. 2018/2019/2020

\textbf{Reunion Scholarship}, Kwansei Gakuin University \hspace{\fill} Mar. 2019

\hrulefill

\begin{flushleft}
  \textbf{\large{Skills}}
\end{flushleft}

Software: R, Stata, Python, QGIS

Languages: English, Japanese

\hrulefill

\begin{flushleft}
  \textbf{\large{Memerships}}
\end{flushleft}

American Economic Association,
Association of Environmental and Resource Economists,
Econometric Society,
Japanese Economic Association,
Society for Environmental Economics and Policy Studies

\end{document}